### 2017-08-22 Paper01_EnthalpyAndCrystallization.tex
Method - EDS - correct errors in SEM equipment types

\subsection{\acrshort{eds} analysis}
Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400, Hitachi, Japan; NanoSEM 230, FEI Nova; NanoSEM 450, FEI Nova). Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.

>>>>

\subsection{\acrshort{eds} analysis}
Alloy composition and homogeneity were confirmed by \acrshort{sem}-\acrshort{eds} (S3400-N, Hitachi, Japan; Nova NanoSEM 230/450, FEI, The Netherlands). Hyper-maps were collected with an accelerating voltage of $15-20kV$, a probe current of $50 \mu A$, counts of 5000 kps or better, dead time less than 20 \%, and working distance was 10mm.
